---
title: "Exploratory Data Analysis - Clothing Reviews"
author: "Atika Dewi Suryni"
date: "`r format(Sys.Date(), '%B %e, %Y')`"
output: 
  html_document:
    theme: flatly
    higlight: zenburn
    toc: true
    toc_float:
      collapsed: false
    number_sections: true
    df_print: paged
    css: assets/style.css
---
<style>
body {
}
</style>


# Background {.tabset}

Hi, we will **study data** that i got from my course

```{r setup}
# clear-up the environment
rm(list = ls())

# chunk options
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  comment = "#>"
)

# scientific notation
options(scipen = 9999)
```

```{r}
# import libs
# if there are libraries are required
```

# Data Study

You can also embed plots, for example:

## Input Data
Make sure our data placed in the same folder our R project data

```{r}
# read data 
clothing <- read.csv("data/clothing_reviews.csv")
```
**Data is ready then we can get started**

# Data Inspection 

```{r}
# check top5 datas
head(clothing)
```
```{r}
# check above5 datas
tail(clothing)
```
```{r}
# check shape of datas
dim(clothing)
```
**From our inspection we can conclude :`clothing` data contain `23486 of rows` and `9 of coloumns`**

```{r}
# check data NA
colSums(is.na(clothing))
```
Check for missing value
```{r}
# remove missing data
# import library 
library(tidyverse)
clothing <- clothing %>% 
  drop_na(division_name, category)

colSums(is.na(clothing))
```

```{r}
# describe column names
names(clothing)
```
* "clothing_id"
* “age_group”
* “review_text”
* “rating”
* “recommended_ind”
* “positive_feedback_count”
* “division_name”
* “category”
* “review_date”

# Data Cleansing and Coertions
Check data type for each column
```{r}
str(clothing)
```

**From this result, we find some of data type not in the correct type. we need to convert it into corect type (data coertion)**

```{r}
# change data type
clothing$review_date <- as.Date(clothing$review_date, "%y/%m/%d")
clothing$age_group <- as.character(clothing$age_group)
clothing$positive_feedback_count <- as.numeric(clothing$positive_feedback_count)


str(clothing)
```

**Each of column already changed into proportional data type**

Now, the data is ready to be procces and analyse

# Data Explanation

```{r}
summary(clothing)
```
* First review was sent on September 2020
* Positive Feedback per day in general has 3 feedbacks per day
* The most category clothing that in sell is tops
* Top customer are in range age 35-53 years old
* In average the product has positive feedback which is 4.00 

# Data Manipulation and Transformation

**check outlier within positive feedback count**
```{r}
aggregate(positive_feedback_count~category, clothing, mean)
```
```{r}
aggregate(positive_feedback_count~category, clothing, var)
```
```{r}
aggregate(positive_feedback_count~category, clothing, sd)
```
```{r}
boxplot(clothing$positive_feedback_count)
```

**Summary : From result above, we find posibilities for the outliers, but from our calculation, Sd value is around 6 ( my oppinion its still be tolerated), so the process may continue**


How much total of rating from each category, and which is the highest?
```{r}
aggregate(rating~category,clothing,sum)
```

**Answer : highest rating comes from category from ‘tops’ in 41777 total ratings**

Which category gives the lowest sales number? how much profit?
```{r}
aggregate(rating~category,clothing,sum)
```

**Answer : lowest rating comes from category from ‘trend’ in 453 total ratings**

Which `product category` based on customer `age_group` gives the highest `positive_feedback_count`? 
```{r}
plot(xtabs(positive_feedback_count~category + age_group,clothing))
```

**Answer : overalll based on `age_group` `35 to 54` and `positive feedback count` category `tops` is the most favourite of consuments**

```{r}
heatmap(xtabs(positive_feedback_count~division_name+category, clothing), cexRow = 0.8, cexCol = 0.8, scale = "column", Colv = NA, Rowv = NA)
```

**Answer : the most lovable category of product is `General`**

In which month, the the consumer give the most rating to the product category (based division_names)? 
```{r}
# create month column
clothing$review_month <- months(clothing$review_date)

# create heatmap to visualize your data
heatmap(xtabs(rating  ~ review_month + age_group,clothing), cexRow = 0.8, cexCol = 0.8, scale = "column", Colv = NA, Rowv = NA)
``` 

**Answer : most of consuments give rating on `August`**



What is the rating activity based on, product category and division_names ? 
```{r}
# scale the consume rating
heatmap(xtabs(rating~category + division_name, clothing), cexRow = 0.8, cexCol = 0.8, scale = "column", Colv = NA, Rowv = NA)
```

**Answer : the highest rating based on division_name and category `General and General Petite` is `Tops` and for `Intimates` is `Intimate`**

What is the most recommended product ? 
```{r}
# scale recommended product
heatmap(xtabs(recommended_ind ~ category + division_name, clothing), cexRow = 0.8, cexCol = 0.8, scale = "column", Colv = NA, Rowv = NA)
```

**Answer : the recommended product based on division_name and category `General and General Petite` is `Tops` and for `Intimates` is `Intimate`**

# Explanatory Text & Business Recomendation

**Recommendations**

- Tops will still be the most lovable category products 
- Brand General and General Petite produce good tops and Intimates produce good Intimate that like by consumers
- August is the month that consumer will leave comment by
- Age group 35 - 64 is the group that have a high engagement with the company
- Q1 is the food time for the company to push the rating especially for age group 25-34, 35-54, 55-64
- Most of highest rating product will be good to be recommended to the non-buyers







